---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tobitext

<!-- badges: start -->
<!-- badges: end -->

`tobitext` is a small R package for simple text analysis workflows. It helps users tokenize text, create bigrams, and visualize the most common bigrams using a tidytext style workflow.

## Installation

You can install the development version of `tobitext` from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("ADC-405-S26/Tokenization-and-Bigrams-Explore-Package")
```

## Why tobitext?

Text analysis can get complicated quickly, especially for beginner NLP projects. This package keeps the workflow small and practical by focusing on three common steps:

- split text into words
- create 2 word phrases (bigrams)
- plot the most common bigrams

## Load the package

```{r example}
library(tobitext)
```

## Example dataset

The package includes a small dataset called `sample_text`.

```{r}
sample_text
```

## Tokenize words

The `tokenize_words()` function turns a text column into one word per row.

```{r}
tokens <- tokenize_words(sample_text, "text")

head(tokens, 10)
```

## Create bigrams

The `create_bigrams()` function creates 2 word combinations from the same text column.

```{r}
bigrams <- create_bigrams(sample_text, "text")

head(bigrams, 10)
```

## Plot top bigrams

The `plot_top_bigrams()` function counts and plots the most common bigrams.

```{r, fig.align='center'}
plot_top_bigrams(bigrams, n = 10)
```

## Package functions

`tobitext` currently includes:

- `tokenize_words()`
- `create_bigrams()`
- `plot_top_bigrams()`
