---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tobitext

<!-- badges: start -->
<!-- badges: end -->

The goal of `tobitext` is to provide simple functions for beginner NLP and text analysis workflows using tidytext.

## Installation

You can install the development version of `tobitext` from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("YOUR_GITHUB_USERNAME/tobitext")
```

## Examples

This is a basic example showing a simple text analysis workflow:

```{r example}
library(tobitext)
```

#### sample_text dataset

```{r}
sample_text
```

#### tokenize_words example

```{r}
tokens <- tokenize_words(sample_text, "text")

tokens
```

#### create_bigrams example

```{r}
bigrams <- create_bigrams(sample_text, "text")

bigrams
```

#### plot_top_bigrams example

```{r, fig.align='center'}
plot_top_bigrams(bigrams)
```
