---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tobitext

<!-- badges: start -->
<!-- badges: end -->

`tobitext` is a small R package for simple text analysis workflows. It helps users tokenize text, create bigrams, and visualize the most common bigrams using a tidytext style workflow.

## Installation

You can install the development version of `tobitext` from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("ADC-405-S26/Tokenization-and-Bigrams-Explore-Package")
```

## Why tobitext?

Modern large language models (LLMs) and NLP systems are fundamentally built on token based text processing. Before models can understand or generate language, text first needs to be broken into smaller units such as words, tokens, or n-grams.

`tobitext` focuses on introducing these foundational NLP concepts through a simple and beginner friendly workflow in R. The package is designed for students and early learners who want to explore how tokenization and bigram analysis work before moving into more advanced machine learning or language modeling tasks.

The package focuses on three core ideas:

- tokenizing text into individual words
- creating bigrams and n-grams
- identifying repeated language patterns

These workflows are commonly used in:

- text mining
- sentiment analysis
- topic discovery
- search engines
- recommendation systems
- chatbot and LLM preprocessing
- predictive text systems

## Load the package

```{r example}
library(tobitext)
```

## Example dataset

The package includes a small dataset called `sample_text` containing short text passages about Lionel Messi and Lisan al Gaib from Dune.

```{r}
sample_text
```

## Tokenize words

Tokenization is one of the first steps in NLP workflows. The `tokenize_words()` function breaks text into individual word level observations.

This process helps transform raw text into structured data that can later be used for:

- word frequency analysis
- text classification
- sentiment analysis
- machine learning workflows
- LLM preprocessing

```{r}
tokens <- tokenize_words(sample_text, "text")

head(tokens, 10)
```

## Create bigrams

Bigrams are 2 word combinations that help capture relationships between words instead of viewing each word independently.

For example, the phrase `"world cup"` contains more meaning together than the individual words `"world"` and `"cup"` separately.

Bigram analysis is commonly used in:

- predictive text systems
- search query analysis
- phrase detection
- recommendation systems
- language modeling

```{r}
bigrams <- create_bigrams(sample_text, "text")

head(bigrams, 10)
```

## Plot top bigrams

The `plot_top_bigrams()` function visualizes the most common bigrams in the dataset.

Finding repeated bigrams helps identify important themes, repeated phrases, and dominant language patterns within text data.

This type of analysis is often used in:

- news and article analysis
- social media mining
- customer review analysis
- topic exploration
- trend detection

```{r, fig.align='center'}
plot_top_bigrams(bigrams, n = 10)
```

## Package functions

`tobitext` currently includes:

- `tokenize_words()`
- `create_bigrams()`
- `plot_top_bigrams()`
