---
title: "tobitext-overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tobitext-overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tobitext)
```
# Overview

`tobitext` is a beginner friendly text analysis package focused on tokenization and bigram analysis workflows.

The package provides simple functions for:

- word tokenization
- bigram creation
- bigram visualization

This vignette demonstrates a complete workflow using the included `sample_text` dataset.

# Example dataset

The package includes a small example dataset called `sample_text`.

```{r}
sample_text
```

# Tokenize text into words

The `tokenize_words()` function converts text into individual word tokens.

```{r}
tokens <- tokenize_words(sample_text, "text")

tokens
```

# Create bigrams

The `create_bigrams()` function creates 2 word combinations from text.

```{r}
bigrams <- create_bigrams(sample_text, "text")

bigrams
```

# Plot common bigrams

The `plot_top_bigrams()` function visualizes the most common bigrams.

```{r}
plot_top_bigrams(bigrams)
```

# Conclusion

`tobitext` provides a simple and beginner friendly workflow for enthusiast to explore text tokenization and bigram analysis in R.
